---
title: Super-Duper Subject
subtitle: Chapter 1. Introduction to Super-Duper Subject
author: Me Myself
date: Department of Statistics | uc3m-Santander Big Data Institute
institute: |
  | Bachelor in Interesting Stuff
  | Last generated: `r Sys.Date()`
output:
  binb::metropolis:
    latex_engine: lualatex
    toc: true
    includes:
      in_header: assets/header.tex
---

```{r,setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, echo=FALSE, message=FALSE)
```

# Section 1

## Subsection 1

::: {.definition data-latex="[Concept 1]"}
A super-important definition of a \alert{concept}.
:::

::: {.example data-latex="[Concept 1 in practice]"}
See the theory in action
:::

## Subsection 1

::: {.examplecont data-latex="[Cont.]"}
We didn't finish, the example continues here!
:::

## Subsection 2

::: {.theorem data-latex="[Fundamental result]"}
Let $X$ be a \alert{random variable},

- we can say **things** about it;
- and even more things.
:::

::: {.proof data-latex="[Proof.]"}
\footnotesize
And here's the proof.
:::

## Subsection 2

::: {.lemma data-latex=""}
A lemma.
:::

::: {.corollary data-latex=""}
Some corollary.
:::

::: {.proposition data-latex=""}
A proposition.
:::

# Section 2

## Subsection 1

Let's introduce the topic...

::: {.example data-latex="[Illustrative example]"}
:::::: {.columns}
::: {.column width="53%"}
\vspace{10pt}
1. Consider this...
2. and that...
3. with an image for further info.
:::
::: {.column width="47%"}
```{r}
#| fig.asp: 1
#| fig.width: 5
boxplot(airquality)
```
:::
::::::
:::

## Summary

- Be sure to include a \alert{summary}.

- A good \alert{summary} is always **enlightening**.
